I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-23 Paper/proofs.tex
fix typos

			\begin{proof}
				First, we show that if one of case 1, 2 happens, then $b$ will not be on a weak compensating pair. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of weak compensating paths 	$(\pi,\pi')$ starting with $a$, with $b$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. A contradiction as 2) $weight({a_j,b})=0$ implies weight$(\pi)=0$.

				Second, we show that if neither 1 nor 2 hold, then $b$ will be on a weak compensating path.
				Because 2) does not hold, there is a $j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
				Because 1) does not hold, $weight({b,z}) \neq 0$, say $>0$.
				Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
				from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
				Then $((a_j,b,z), \pi')$ is also a weak compensating pair. \qed
			\end{proof}

>>>>

			\begin{proof}
				First, we show that if one of case 1, 2 happens, then $b$ will not be in a weak compensating pair. If 1), it is obvious. For 2, we reason by contradiction: assume there is a pair of weak compensating paths 	$(\pi,\pi')$ starting with $a$, with $b$ in $\pi$ and weight$(\pi) > 0$. It means that $a \in J$. This is a contradiction as 2) $weight({a_j,b})=0$ implies weight$(\pi)=0$.

				Second, we show that if neither 1 nor 2 hold, then $b$ will be in a weak compensating path.
				Because 2) does not hold, there exists $j \in J$ with $weight({a_j,b}) \neq 0$, say $>0$.
				Because 1) does not hold, $weight({b,z}) \neq 0$, say $>0$.
				Now, by definition of $J$, there is a pair of weak compensating paths $\pi,\pi'$ 
				from $a_j$ to $z$, say with $\pi'$ with weight $<0$.
				Then two paths $(a_j,b,z)$ and $\pi'$ also form a weak compensating pair. \qed
			\end{proof}
